### 2013-10-21 article.tex
Wrote draft result-section.

\subsubsection{Computational~Precision}
\label{sec:contribution:results:computationalprecision}
\begin{table}
\begin{center}
	\begin{tabular}{|r|r|r|}
		\hline
		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
		0.0     			& ~0.01   			& ~0.0025            		\\ \hline
	\end{tabular}
\label{tab:contribution:results:computationalprecision:avgprecision}
\caption {Average precisional deviations in floating point operations.}
\end{center}
\end{table}

%http://msdn.microsoft.com/en-us/library/windows/desktop/cc308050%28v=vs.85%29.aspx
Integer had no loss of precision whatsoever.
All floating point experiments experienced a minimum precisional deviation of 0, a maximum precisional deviation of ~0.01 and a standard precisional deviation of ~0.0025. Experiments indicated no increased performance loss in-between the different driver types.

>>>>

\subsubsection{Computational~Precision}
Integer~precision calculation showed no sign of loss of precision whatsoever. Meanwhile, all floating~point-experiments experienced an equal average loss of computational precision. However, the data collected indicates no divergence in the precisional loss of respective subject. The average deviations in precision experienced equally with each configuration, in relation to the $Ref$-matrix descibed in Section~\ref{sec:contribution:method}, are presented in Table~\ref{tab:contribution:results:computationalprecision:avgprecision}. See Microsoft's documentation on Floating-point Rules\footnote{Microsoft's reference on Floating-Point~Rules:~\url{http://bit.ly/1bOQnZu}. Retrieved 21-10-2013.} for more information surrounding floating~point-precision in the \textit{Direct3D}-framework.
\label{sec:contribution:results:computationalprecision}
\begin{table}[hbt]
\begin{center}
	\begin{tabular}{|r|r|r|}
		\hline
		\textbf{Minimum} 	& \textbf{Maximum} 	& \textbf{Standard} 	\\ \hline
		0.0     			& ~0.01   			& ~0.0025            		\\ \hline
	\end{tabular}
\label{tab:contribution:results:computationalprecision:avgprecision}
\caption {Average precisional deviations in floating~point-operations.}
\end{center}
\end{table}

%http://msdn.microsoft.com/en-us/library/windows/desktop/cc308050%28v=vs.85%29.aspx
